Probabilities and propensities: conversion experiences in online grocery shopping

### 2017-03-28 lists_conversion_experience.rmd
preparing submission branch

---
title: "Probabilities and propensities: conversion experiences in online grocery shopping"
author: "Adrian Mackenzie"
date: "`r Sys.Date()`"
output:
tufte::tufte_handout: default
fontsize: 12pt
citation_package: biber
latex_engine: xelatex
bibliography: /home/mackenza/ref_bibs/uni.bib
csl: "sage-harvard.csl"
link-citations: yes
header-includes:
    - \usepackage{setspace}
    - \doublespacing
---

@@

# Abstract

We can understand devices such as recommender systems as attempts to transform or convert the temporal and agential fabric of social ordering practices. 
This paper investigates practices of ordering in the setting of shopping lists and  online grocery orders. 
Although all shopping lists mix past and future actions, actual and potential events, and normative and actual values, their re-writing by recommender systems adds a new operational dynamic.
It reconstructs an account of how a recommender system suggests a small number of grocery items of personal relevance to each of the millions of online grocery shoppers in  a major UK supermarket chain. 
The paper explores how the constitutive incompleteness of shopping lists, their propensity to expand or change, becomes more important than their capacity to  enumerate or rank things. 
It argues that the conversion of lists from finite ordering to indeterminate propensity in recommender systems requires new ways of conceptualising social order.

>>>>

---
title: "Probabilities and propensities: conversion experiences in online grocery shopping"
author: Adrian Mackenzie^[University of Somewhere] 
date: "`r format(Sys.time(), '%B %Y')`"
fontsize: 12pt
citation_package: biber
latex_engine: xelatex
bibliography: /home/mackenza/ref_bibs/uni.bib
csl: "sage-harvard.csl"
link-citations: yes
header-includes:
    - \usepackage{setspace}
    - \doublespacing
abstract: 
    "Recommender systems attempt to transform or convert the temporal and agential fabric of social ordering by substituting probabilistic calculation for social practices. This paper investigates practices of ordering in the setting of shopping lists and  online grocery orders. It reconstructs an account of how a recommender system suggests a small number of grocery items of personal relevance to each of the millions of online grocery shoppers in  a major UK supermarket chain. Although all shopping lists mix past and future actions, actual and potential events, and normative and actual values, their re-writing by recommender systems adds a new operational dynamic.The paper explores how in the context of recommender systems the constitutive incompleteness of shopping lists, their propensity to expand or change, becomes more important than their capacity to inscribe social order. This suggests that the conversion of lists from finite ordering to indeterminate propensity in recommender systems requires new ways of conceptualising social order."
keywords: prediction, probability, order, recommender system, shopping
---

@@
